A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-10-17 paper.tex
Fixed Table I

    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
    Norm                       & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
    $\epsilon$                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$ \\
    Max error              & 90.24       & 66.79           & 99.63       & 70.47          \\ 
    Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\ 
    Peak memory usage      & 80B          & 80B             & 432B        & 240B           \\ 
    Processing time        & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms        \\ \hline
    \end{tabular}
    \caption{5-times bicep curl (2D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
    Norm               & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$             & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ 
    Max error              & 99.49     & 70.52             & 99.99      & 70.71             \\ 
    Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ 
    Peak memory       & 80B        & 80B               & 2.1KB      & 1.3KB             \\ 
    Processing time      & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
    \end{tabular}
    \caption{Mohammad lateral biceps curl (2D)}
    \end{subfigure}\\    
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                            & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$             & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$   \\ 
    Max error              & 100.17       & 60.38           & 99.94       & 56.89            \\ 
    Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\ 
    Peak memory            & 112B         & 112B            & 384B        & 256B             \\ 
    Processing time        & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms          \\ \hline
    \end{tabular}
    \caption{5-times biceps curl (3D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$                & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\
    Max error                 & 97.54     & 56.00             & 99.99      & 57.73             \\
    Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\
    Peak memory & 112B        & 112B              & 4.9KB      & 3.0KB             \\
    Processing time           & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
    \end{tabular}
    \caption{Mohammad lateral biceps curl (3D)}
    \end{subfigure}
    \caption{Validation experiment}
    \label{table:results-validation}
\end{table}

>>>>

    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
    $\epsilon$                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$ \\
    Max error              & 99.88       & 70.68           & 99.63       & 70.47          \\ 
    Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\ 
    Peak memory usage      & 80B          & 80B             & 432B        & 240B           \\ 
    Processing time        & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms        \\ \hline
    \end{tabular}
    \caption{5-times bicep curl (2D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                   & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$             & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ 
    Max error              & 99.99     & 70.71             & 99.99      & 70.71             \\ 
    Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ 
    Peak memory       & 80B        & 80B               & 2.1KB      & 1.3KB             \\ 
    Processing time      & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
    \end{tabular}
    \caption{Mohammad lateral biceps curl (2D)}
    \end{subfigure}\\    
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                            & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$             & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$   \\ 
    Max error              & 99.88       & 57.41           & 99.94       & 56.89            \\ 
    Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\ 
    Peak memory            & 112B         & 112B            & 384B        & 256B             \\ 
    Processing time        & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms          \\ \hline
    \end{tabular}
    \caption{5-times biceps curl (3D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$                & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\
    Max error                 & 99.96     & 57.73             & 99.99      & 57.73             \\
    Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\
    Peak memory & 112B        & 112B              & 4.9KB      & 3.0KB             \\
    Processing time           & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
    \end{tabular}
    \caption{Mohammad lateral biceps curl (3D)}
    \end{subfigure}
    \caption{Validation experiment}
    \label{table:results-validation}
\end{table}
